Mispronunciation Sensitivity Publication Bias for CogSci

### 2018-02-05 Analyses.Rmd
Created CogSci markdown files for Analysis and Publication Bias
Markdown files have been uploaded to OSF CogSci Subproject.

sum_dat <- dat[!duplicated(dat[c("short_cite", "same_infant")]),]
time_wind_dat <- dat[!duplicated(dat[c("short_cite", "offset", "post_nam_dur")]),]
distract_dat <- dat[!duplicated(dat[c("short_cite", "object_pair")]),]

@@

>>>>

sum_dat <- dat[!duplicated(dat[c("short_cite", "same_infant")]),]
time_wind_dat <- dat[!duplicated(dat[c("short_cite", "offset", "post_nam_dur")]),]
distract_dat <- dat[!duplicated(dat[c("short_cite", "object_pair")]),]
mix_co_mp <- dat[!duplicated(dat[c("short_cite", "word_correct_and_MP")]),]

@@

This is a summary of whether an experiment had both correct and mispronounced versions of the word in the experiment

```{r DescriptivesCoMp, echo = FALSE}
#What kind of distractor was used?

mix_info <- mix_co_mp %>%
  group_by(word_correct_and_MP) %>%
  summarize(count = n())

kable(mix_info)

### 2018-02-05 CogSci_Analyses.Rmd
Created CogSci markdown files for Analysis and Publication Bias
Markdown files have been uploaded to OSF CogSci Subproject.

---
title: "MP MetaAnalysis"
author: "Christina Bergmann"
output: 
  pdf_document:
    toc: true
---
```{r Setup, echo = FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, tidy = TRUE, message = FALSE, error = TRUE)

@@

sum_dat <- dat[!duplicated(dat[c("short_cite", "same_infant")]),]
time_wind_dat <- dat[!duplicated(dat[c("short_cite", "offset", "post_nam_dur")]),]
distract_dat <- dat[!duplicated(dat[c("short_cite", "object_pair")]),]
mix_co_mp <- dat[!duplicated(dat[c("short_cite", "word_correct_and_MP")]),]

@@

# Descriptive data

The database contains data from `r length(unique(dat$short_cite))` papers consisting of data from `r sum(sum_dat$n_1)` infants. In the tables below, we provide more descriptive information.

@@

pub_info <- dat %>%
  group_by(publication_status) %>%
  summarize(n_unique = n_distinct(short_cite), count = n())

@@

The table below shows based on which data we calculated effect sizes.

@@

es_info <- dat %>%
  group_by(es_method) %>%
  summarize(n_unique = n_distinct(short_cite), count = n())

@@

We also have different ways of comparison of the time-course data, as the next table shows.
```{r DescriptivesComparison, echo = FALSE}
db_ET_correct$within_measure_descriptive <- ifelse(db_ET_correct$within_measure == "post",
 "post-naming phase compared with chance (=50%)",
ifelse(db_ET_correct$within_measure == "pre_post", "post-naming compared to pre-naming phase", "post-pre difference score compared with chance (=0)"))

comparison_info <- db_ET_correct %>%
  group_by(within_measure_descriptive) %>%
  summarize(n_unique = n_distinct(short_cite), count = n())

This is a summary of the type of distractor used in an experiment

@@

This is a summary of whether an experiment had both correct and mispronounced versions of the word in the experiment

```{r DescriptivesCoMp, echo = FALSE}
#What kind of distractor was used?

mix_info <- mix_co_mp %>%
  group_by(word_correct_and_MP) %>%
  summarize(count = n())

kable(mix_info)

## Analysis time window

Where possible, we noted the time window for analysis. First, let's look at the offset (in milliseconds) after the start of the word, i.e. the begin of a give analysis window for a naming effect

```{r TimeWindowOffset}
offset_info <- time_wind_dat %>%
  group_by(offset) %>%
  summarize(count = n())

kable(offset_info)

Next we look at duration (in seconds) of the post naming window, here,too, we see a lot of heterogeneity.

```{r TimeWindowduration}
duration_info <- db_ET_correct %>%
  group_by(post_nam_dur) %>%
  summarize(count = n())

kable(duration_info)

In summary, we see little consistency in analysis methods of comparable studies looking at naming and mispronunciation effects.

## Early Ages
Even the youngest ages in the database (less than 1 year) show mispronunciation sensitivity

unique(youngest$short_cite)
youngest$cond_lab <- ifelse(youngest$condition == 1, "correct", "misp")
ggplot(youngest, aes(x=cond_lab, y = g_calc, color = cond_lab)) + geom_boxplot()

## Correct object identification effect

rma_correct_age = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_correct, random = ~ collapse | short_cite)

## Mispronunciation object identification effect

## Mispronunciation effect
```{r MPEffect}
db_ET_correct$condition <- 1
db_ET_MP$condition <- 0

rma_MPeffect_1 <- rma.mv(g_calc, g_var_calc, mods = ~condition-1, data = dat, random = ~ collapse | short_cite)

summary(rma_MPeffect_1)

### Language effect

Followup: Per condition (correct or MP) the interaction with age

```{r LanguageEffectAnalyses}
dat$condition_label = ifelse(dat$condition==1, "Correct", "Misp")

dat$lang_family = ifelse(dat$native_lang=="American English" | dat$native_lang=="British English" |
                           dat$native_lang=="Dutch" | dat$native_lang=="English" | 
                           dat$native_lang=="Danish" | dat$native_lang=="Swedish" |
                           dat$native_lang=="German", "Germanic",
                         ifelse(dat$native_lang == "French" | dat$native_lang == "Catalan" |
                                  dat$native_lang == "Spanish" | dat$native_lang == "Catalan-Spanish" |
                                  dat$native_lang == "Swiss French", "Romanic", "Sino-Tibetian"))

rma_lang_interaction <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*lang_family, data = dat, random = ~ collapse | short_cite)
summary(rma_lang_interaction)
```

### Type of distractor

@@

## Type of Distractor with age
```{r DistractorTypeAge}

rma_DistractorAge <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*as.factor(object_pair), data = dat, random = ~ collapse | short_cite)

summary(rma_DistractorAge)

@@

#### Subset to same age range

min_age <- min(dat[dat$object_pair=="familiar_novel",]$mean_age_1)
max_age <- max(dat[dat$object_pair=="familiar_novel",]$mean_age_1)

dat_age= dat%>%
  filter(mean_age_1>min_age&mean_age_1<max_age)

rma_DistractorAgeS <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*as.factor(object_pair), data = dat_age, random = ~ collapse | short_cite)

summary(rma_DistractorAgeS)

### Distractor Overlap

```{r DistractorOverlap}

rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~age.C*distractor_overlap, data = db_ET_MP, random = ~ collapse | short_cite)

summary(rma_DistractorOverlap)

## Number of features

```{r NFeatures}

db_ET_MPf = db_ET_MP %>%
  filter(n_feature != "1-3" & n_feature != "1-2" & n_feature != "2-3")

#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature), data = db_ET_MPf, random = ~collapse | short_cite)

summary(rma_NFeatures)

rma_NFeaturesAge <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature)*age.C, data = db_ET_MPf, random = ~collapse | short_cite)

summary(rma_NFeaturesAge)
```

### Interaction with condition

```{r NFeaturesCondition}

dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
                n_feature == "2" | n_feature == "3")

#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature)*condition, data = dat_f, random = ~collapse | short_cite)

summary(rma_NFeatures)

rma_NFeaturesAge <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature)*age.C*condition, data = dat_f, random = ~collapse | short_cite)

summary(rma_NFeaturesAge)
```

## MP location

```{r Location}
#table(db_ET_MP$mispron_location)

db_ET_MPl = db_ET_MP %>%
  filter(mispron_location == "onset"  | mispron_location == "medial")

#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
rma_Location <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location, data = db_ET_MPl, random = ~collapse | short_cite)

summary(rma_Location)

rma_LocationAge <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location*age.C, data = db_ET_MPl, random = ~collapse | short_cite)

summary(rma_LocationAge)
```

## MP type: Vowel, consonant, or tone?

```{r MPtype}
db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" )

rma_TypeFeaturesMP <- rma.mv(g_calc, g_var_calc, mods = ~type_feature, data = db_MP_type, random = ~collapse | short_cite)

summary(rma_TypeFeaturesMP)

rma_TypeFeaturesMPAge <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*age.C, data = db_MP_type, random = ~collapse | short_cite)

summary(rma_TypeFeaturesMPAge)
```

### Interaction with condition
```{r MPtypeCondition}
dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" |
                type_feature == "tone")
dat_type$type_feature <- as.factor(ifelse(dat_type$condition == 1, "none", dat_type$type_feature))

rma_TypeFeatures <- rma.mv(g_calc, g_var_calc, mods = ~relevel(type_feature, "none")*condition, data = dat_type, random = ~collapse | short_cite)

summary(rma_TypeFeatures)

rma_TypeFeaturesAge <- rma.mv(g_calc, g_var_calc, mods = ~relevel(type_feature, "none")*age.C*condition, data = dat_type, random = ~collapse | short_cite)

summary(rma_TypeFeaturesAge)
```

### Interaction with language
```{r MPtypeLanguage}
#dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" |
#                type_feature == "tone")

dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")

dat_type$type_feature <- as.factor(ifelse(dat_type$condition == 1, "none", dat_type$type_feature))

dat_type$lang_family = ifelse(dat_type$native_lang=="American English" | dat_type$native_lang=="British English" | dat_type$native_lang=="Dutch" |
dat_type$native_lang=="Danish" | dat_type$native_lang=="Swedish" |
dat_type$native_lang=="English" | dat_type$native_lang=="German", "Germanic", ifelse(dat_type$native_lang == "French" | dat_type$native_lang == "Catalan" | dat_type$native_lang == "Spanish" | dat_type$native_lang == "Catalan-Spanish" | dat_type$native_lang == "Swiss French", 
                                "Romanic", "Sino-Tibetian"))

dat_type_sub <- subset(dat_type, lang_family != "Sino-Tibetian")

rma_TypeFeatures_Lang <- rma.mv(g_calc, g_var_calc, mods = ~relevel(type_feature, "none")*lang_family, data = dat_type_sub, random = ~collapse | short_cite)

summary(rma_TypeFeatures_Lang)
```

### Interaction with condition and language
```{r MPtypeLanguageCondition}
dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")# |
                #type_feature == "tone")
dat_type$type_feature <- as.factor(ifelse(dat_type$condition == 1, "none", dat_type$type_feature))

dat_type$lang_family = ifelse(dat_type$native_lang=="American English" | dat_type$native_lang=="British English" | dat_type$native_lang=="Dutch" |
dat_type$native_lang=="Danish" | dat_type$native_lang=="Swedish" |
dat_type$native_lang=="English" | dat_type$native_lang=="German", "Germanic", ifelse(dat_type$native_lang == "French" | dat_type$native_lang == "Catalan" | dat_type$native_lang == "Spanish" | dat_type$native_lang == "Catalan-Spanish" | dat_type$native_lang == "Swiss French", 
                                "Romanic", "Sino-Tibetian"))

dat_type_sub <- subset(dat_type, lang_family != "Sino-Tibetian")
dat_type_sub$lang_family <- as.factor(dat_type_sub$lang_family)

rma_TypeFeatures_Lang <- rma.mv(g_calc, g_var_calc, mods = ~relevel(type_feature, "none")*lang_family*condition, data = dat_type_sub, random = ~collapse | short_cite)

summary(rma_TypeFeatures_Lang)

```
## Correlation MP effect and vocabulary

First, let's take a look at which vocabulary data we have available.

```{r VocabularyData}
vocab_info <- db_ET_correct %>%
  mutate(has_vocab = ifelse(!is.na(r_comprehension), "comprehension", 
                            ifelse(!is.na(r_production), "production", "none"))) %>%
  group_by(has_vocab) %>%
  summarize(count = n())

We have 17 correlations, roughly evenly divided between comprehension and production data. There is reason to believe that production data are different from comprehension data (the former being easier to estimate for parents in the typical questionnaire-based assessment), so we should both analyze this data separately and see whether it makes sense in a joint analysis.

```{r ComprehensionMeta}
#we're relying on the library meta function metacor
compr  <- subset(db_ET_correct, !is.na(db_ET_correct$r_comprehension) & r_comprehension > -1)

metacor(cor=r_comprehension, n=n_1, studlab = short_cite, data = compr, sm = "COR")
```

```{r ProductionMeta}
#we're relying on the library meta function metacor
prodr  <- subset(db_ET_correct, !is.na(db_ET_correct$r_production) & r_production < 1)

metacor(cor=r_production, n=n_1, studlab = short_cite, data = prodr, sm = "COR")
```

# Plotting
```{r PlotAPATheme}
#Themes and plot
apatheme=theme_bw()+
  theme(#panel.grid.major=element_blank(),
    #panel.grid.minor=element_blank(),
    #panel.border=element_blank(),
    axis.line=element_line(),
    text=element_text(family='Times', size=25))

```
## Mispronunciation Effect by Age (color)
```{r PlotMPEffect}

min(dat$mean_age_1/30.44)
max(dat$mean_age_1/30.44)

  jpeg(filename = "figures/AgeEffect_log.jpg", 
       width = 600, height = 400, units = "px")

  dev.off()

```
## Mispronunciation Effect by Age (bw)
```{r PlotMPEffect_BW}

p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  geom_point(aes(size = weights_g, shape=condition_label, color=condition_label),
             show.legend=FALSE) + 
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
  scale_color_grey()+
  theme_bw()+
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/AgeEffect_log_BW.jpg", p,height= 3,width= 6)

## MP type: Consonant, Vowel, or Tone?
```{r PlotCVEffect}

p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  geom_point(aes(size = weights_g, shape = type_feature),show.legend=FALSE) + 
  facet_grid(.~type_feature)+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  theme(text = element_text(size=16)) + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/AgeEffect_log_CV.jpg", p)
```

## Language Family by MP type: Consonant, Vowel, or Tone?
```{r PlotCVEffect_Lang}

p <- ggplot(dat, aes(type_feature, g_calc, color = type_feature)) + 
  geom_boxplot() + 
  facet_grid(lang_family~condition_label)+
  #geom_line(y= 0, linetype="dotted") + 
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  theme(text = element_text(size=16)) + 
  xlab("Language Family") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/LangFamily_CV.jpg", p)
```

## Number of Features
```{r PlotFeatEffect}

#dat_f <- subset(dat, n_feature == "0" | n_feature == "1" | n_feature == "2" | n_feature == "3")

p <- ggplot(dat_f, aes(mean_age_1/30.44, g_calc, color = n_feature)) + 
  geom_point(aes(size = weights_g, shape = n_feature),show.legend=FALSE) + 
  #facet_grid(.~type_feature)+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  theme(text = element_text(size=16)) + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/AgeEffect_log_feat.jpg", p)

## Position of Mispronunciation
```{r PlotPositionEffect}

dat.p <- subset(dat, mispron_location == "onset" | mispron_location == "medial" |
                mispron_location == "offset")

p <- ggplot(dat.p, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  geom_point(aes(size = weights_g, shape = mispron_location),show.legend=FALSE) + 
  facet_grid(.~mispron_location)+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  theme(text = element_text(size=16)) + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/AgeEffect_log_position.jpg", p)

## Distractor Familiarity
```{r PlotDistFamEffect}

dat$condition_label = ifelse(dat$condition==1, "correct", "MP")
dat$dist_code <- ifelse(dat$object_pair == "familiar_familiar", "familiar", "unfamiliar")

p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  geom_point(aes(size = weights_g, shape = dist_code),show.legend=FALSE) + 
  facet_grid(.~dist_code)+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_color_manual(values=wes_palette(name="Darjeeling"))+
  theme_bw()+
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/AgeEffect_log_distractor_fam.jpg", p)

## Distractor Familiarity (w/o age)
```{r PlotDistFamEffect_NoAge}

dat$condition_label = ifelse(dat$condition==1, "correct", "MP")
dat$dist_code <- ifelse(dat$object_pair == "familiar_familiar", "familiar", "unfamiliar")

ggsave("figures/Distractor_fam_log.jpg", p)

## Distractor Familiarity (w/o age, subset to age range)
```{r PlotDistFamEffect_NoAge_AgeMatch}

min_age<-min(dat[dat$object_pair=="familiar_novel",]$mean_age_1)
max_age <- max(dat[dat$object_pair=="familiar_novel",]$mean_age_1)

dat_age= dat%>%
  filter(mean_age_1>min_age&mean_age_1<max_age)

dat_age$condition_label = ifelse(dat_age$condition==1, "correct", "MP")
dat_age$dist_code <- ifelse(dat_age$object_pair == "familiar_familiar", "familiar", "unfamiliar")

p <- ggplot(dat_age, aes(dist_code, g_calc, color = condition_label)) + 
  geom_boxplot() + 
  #geom_line(y= 0, linetype="dotted") + 
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_color_manual(values=wes_palette(name="Darjeeling"))+
  theme_bw()+
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Distractor Familiarity") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/AgeMatch_Distractor_fam_log.jpg", p)

## Overlap between distractor and target

```{r PlotDistOverlapEffect}

p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  geom_point(aes(size = weights_g, shape = distractor_overlap),show.legend=FALSE) + 
  facet_grid(.~distractor_overlap)+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  theme(text = element_text(size=16)) + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/AgeEffect_log_distractor_overlap.jpg", p)

## Language Family
```{r PlotLanguageEffect}

dat$lang_family = ifelse(dat$native_lang=="American English" | dat$native_lang=="British English" |
                           dat$native_lang=="Dutch" | dat$native_lang=="English" | 
                           dat$native_lang=="German", "Germanic",
                         ifelse(dat$native_lang == "French" | dat$native_lang == "Catalan" |
                                  dat$native_lang == "Spanish" | dat$native_lang == "Catalan-Spanish" |
                                  dat$native_lang == "Swiss French", "Romanic", "Sino-Tibetian"))

p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  geom_point(aes(size = weights_g, shape = lang_family),show.legend=FALSE) + 
  facet_grid(.~lang_family)+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  theme(text = element_text(size=16)) + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/AgeEffect_log_language.jpg", p)

>>>>

---
title: "Mispronunciation MetaAnalysis for CogSci"
author: "Christina Bergmann and Katie Von Holzen"
output: 
  pdf_document:
    toc: true
---
```{r Setup, echo = FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, tidy = TRUE, message = FALSE, error = TRUE)

@@

sum_dat <- dat[!duplicated(dat[c("short_cite", "same_infant")]),]
time_wind_dat <- dat[!duplicated(dat[c("short_cite", "offset", "post_nam_dur")]),]
distract_dat <- dat[!duplicated(dat[c("short_cite", "object_pair")]),]
mix_co_mp <- dat[!duplicated(dat[c("short_cite", "word_correct_and_MP")]),]
vocab_dat <- dat[!duplicated(dat[c("short_cite")]),]

@@

# Systematic Study Collection

The database contains data from `r length(unique(dat$short_cite))` papers consisting of data from `r sum(sum_dat$n_1)` infants.

@@

pub_info <- dat %>%
  group_by(publication_status) %>%
  summarize(n_unique = n_distinct(short_cite))

@@

# Effect Size Calculation

## Type of Dependent Variable

The table below summarized the type of dependent variable and subsequent comparison reported in each paper.

```{r DescriptivesComparison, echo = FALSE}
db_ET_correct$within_measure_descriptive <- ifelse(db_ET_correct$within_measure == "post",
 "post-naming phase compared with chance (=50%)",
ifelse(db_ET_correct$within_measure == "pre_post", "post-naming compared to pre-naming phase", "post-pre difference score compared with chance (=0)"))

comparison_info <- db_ET_correct %>%
  group_by(within_measure_descriptive) %>%
  summarize(n_unique = n_distinct(short_cite))

## Data Used to Calculate Effect Sizes

The table below shows based on which data we calculated effect sizes. If both raw means/standard deviations as well as t-values were available, we used raw means/standard deviations to calculate effect sizes.

@@

es_info <- dat %>%
  group_by(es_method) %>%
  summarize(n_unique = n_distinct(short_cite))

@@

## Object Identification

### Correct words

Meta-analytic effect for correctly pronounced words in object identification.

### Mispronounced words

Meta-analytic effect for mispronounced words in object identification.

## Mispronunciation Sensitivity

Meta-analytic effect for mispronunciation senstivity.

```{r MPEffect}
db_ET_correct$condition <- 1
db_ET_MP$condition <- 0

## Age Moderator Effects

### Object identification correct words

Age moderator effects for object identification for correctly pronounced words.

```{r MAcorrect_age}
rma_correct_age = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_correct, random = ~ collapse | short_cite)

### Object identification mispronounced words

Age moderator effects for object identification for mispronounced words.

```{r MAMP_age}

### Mispronunciation sensitivity

Age moderator effects for mispronunciation sensitivity

```{r MPEffect_age}
db_ET_correct$condition <- 1
db_ET_MP$condition <- 0

# Plotting Mispronunciation Sensitivity by Age

This is the plot used in Figure 2. Effect sizes for correct pronunciations (yellow) and mispronunciations (blue) by participant age. Point size is inverse variance. The dashed line indicates zero.

```{r FunnelPrep, echo = FALSE}

#Themes and plot
apatheme=theme_bw()+
  theme(#panel.grid.major=element_blank(),
    #panel.grid.minor=element_blank(),
    #panel.border=element_blank(),
    axis.line=element_line(),
    text=element_text(family='Times', size=25),
    legend.position='none')

```{r PlotMPEffect, echo = FALSE}

#p

#min(dat$mean_age_1/30.44)
#max(dat$mean_age_1/30.44)

  #jpeg(filename = "figures/AgeEffect_log.jpg", 
 #      width = 600, height = 400, units = "px")

  #dev.off()

# Supplementary Analyses for Discussion

This section includes supplementary analyses discussed in the Discussion section

## Vocabulary Data Available

This table summarizes which papers also measured vocabulary in the infants they tested.

```{r VocabularyData}

vocab_info <- vocab_dat %>%
  mutate(has_vocab = ifelse(!is.na(r_comprehension) & !is.na(r_production), "comprehension & production", 
                            ifelse(!is.na(r_comprehension), "just comprehension",
                            ifelse(!is.na(r_production), "just production", "none")))) %>%
  group_by(has_vocab) %>%
  summarize(count = n())

## Mispronunciation Sensitivity at Youngest Ages

Mispronunciation sensitivity in the papers in our dataset with the youngest ages (< 12-months-of-age; Bergelson & Swingley, 2017; Mani & Plunkett, 2007; Zesiger et al., 2012).

#unique(youngest$short_cite)
youngest$cond_lab <- ifelse(youngest$condition == 1, "correct", "misp")
p <- ggplot(youngest, aes(x=cond_lab, y = g_calc, color = cond_lab)) + geom_boxplot()

## Known vs Novel Distractor Images

This table summarizes which papers used a known or novel distractor image.

@@

### Does distractor familiarity (known vs. novel) impact mispronunciation sensitivity?

Preliminary moderator test examining the influence of distractor familiarity on mispronunciation sensitivity

@@

## Plotting Influence of Distractor Familiarity

```{r PlotDistFamEffect_NoAge, echo = FALSE}

dat$condition_label = ifelse(dat$condition==1, "correct", "mispronunciation")
dat$dist_code <- ifelse(dat$object_pair == "familiar_familiar", "known", "novel")

#ggsave("figures/Distractor_fam_log.jpg", p)

@@

### 2018-02-05 CogSci_Publication_bias.Rmd
Created CogSci markdown files for Analysis and Publication Bias
Markdown files have been uploaded to OSF CogSci Subproject.

---
title: "MP Publication Bias"
author: "originally Christina Bergmann, modified by Katie Von Holzen"
output: 
  pdf_document:
    toc: true
---
```{r Setup, echo = FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, tidy = TRUE, message = FALSE, error = TRUE)

@@

#Preparation

Read in data and tidy up dataset

@@

# Funnel Plot Asymmetry
Use ranktest() to check for funnel plot asymmetry. All three tests show evidence of significant asymmetry.

```{r FunnelPlotAsymmetry, echo = FALSE}

# Publication bias can become visible in funnel plot asymmetry. 
# Metafor comes with several options to check this, I chose ranktest and regtest

# this is the model of the mispronunciation effect, without age
ranktest(rma_MPeffect)

# correct object identification
ranktest(rma_correct)

@@

# Export data for p-curve

These files can be found in "p_curve_app/"

for correct: p_curve_co.txt
for mispronounced: p_curve_mp.txt

NOTE: This will always append lines to the existing txt file, check for double writing!

for(line in 1:length(db_ET_MP$n_1)){
  if(!is.na(db_ET_MP[line,]$t)){
    newline = paste("t(", db_ET_MP[line,]$n_1-1, ")=",db_ET_MP[line,]$t, sep = "")
    write(newline, file = textfile_mp, append = TRUE)
    #cat("\n")
    #write(newline, file = textfile, append = TRUE)    
  }
}
```

# What is the power of the studies in the dataset?

```{r Power_exist, echo = FALSE}
d = rma.mv(g_calc, g_var_calc, data = db_mpe, random = ~ 1 | short_cite)$b[,1]

# estimate from mispronunciation sensitivity
mp_est <- coef(summary(rma_MPeffect))[2,]$estimate

pwr.t.test(n = median(db_mpe$n_1, na.rm=TRUE), d = mp_est, sig.level = .05, type = "paired", alternative = "two.sided")

# What is the average power to detect a mispronunciation sensitivity effect (to be compared with p-curve estimate)
```{r Power_plan, echo = FALSE}

# estimate from mispronunciation sensitivity
mp_est <- coef(summary(rma_MPeffect))[2,]$estimate

@@

### Plots from Sakaluk, 2016
### https://sakaluk.wordpress.com/2016/02/16/7-make-it-pretty-plots-for-meta-analysis/

@@

#Call the pretty funnel plot
fp_co +   ggtitle("Correct")
ggsave("figures/FunnelPlot_correct.pdf")
```

@@

  #Store the meta-analytic estimate and its standard error from whatever model you run (substitute your own values)
  summary(rma_MP)
  estimate_mp = coef(summary(rma_MP))$estimate
  se_mp = coef(summary(rma_MP))$se

@@

  #Call the pretty funnel plot
  fp_mp + ggtitle("Mispronunciation")
  ggsave("figures/FunnelPlot_misp.pdf")

@@

@@

  jpeg(filename = "figures/Funnel_Plots_Object_Identification.jpg", 
       width = 600, height = 400, units = "px")

@@

  dev.off()

@@

>>>>

---
title: "Mispronunciation Sensitivity Publication Bias for CogSci"
author: "Christina Bergmann and Katie Von Holzen"
output: 
  pdf_document:
    toc: true
---
```{r Setup, echo = FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, tidy = TRUE, message = FALSE, error = TRUE)

@@

# Preparation
Read in data and tidy up dataset

@@

# Funnel Plot Asymmetry
Use ranktest() to check for funnel plot asymmetry. Both tests show evidence of significant asymmetry.

## Object Identification Correct Words

```{r FunnelPlotAsymm_correct, echo = FALSE}

# Publication bias can become visible in funnel plot asymmetry. 
# Metafor comes with several options to check this, I chose ranktest and regtest
# correct object identification
ranktest(rma_correct)

## Object Identification Mispronounced Words

```{r FunnelPlotAsymm_misp, echo = FALSE}

@@

@@

### Plots adapted from Sakaluk, 2016, see also Black & Bergmann, 2017
### https://sakaluk.wordpress.com/2016/02/16/7-make-it-pretty-plots-for-meta-analysis/

@@

#Call the pretty funnel plot
fp_co +   ggtitle("Correct")
#ggsave("figures/FunnelPlot_correct.pdf")

@@

  #Store the meta-analytic estimate and its standard error from whatever model you run (substitute your own values)
  #summary(rma_MP)
  estimate_mp = coef(summary(rma_MP))$estimate
  se_mp = coef(summary(rma_MP))$se

@@

  #Call the pretty funnel plot
  fp_mp + ggtitle("Mispronunciation")
#  ggsave("figures/FunnelPlot_misp.pdf")

@@

Below is the plot used in Figure 1. Funnel plots for object identification for correct (left) and mispronounced (right) words, plotting the standard error of the effect size in relation to effect size. The black line marks zero, the dashed grey line marks the effect estimate, and the grey line marks funnel plot asymmetry.

@@

#  jpeg(filename = "figures/Funnel_Plots_Object_Identification.jpg", 
#       width = 600, height = 400, units = "px")

@@

#  dev.off()

@@

# P-curve

## Export Data for P-curve

for correct word object identification see "p_curve_co.txt" file

for mispronounced word object identification see "p_curve_mp.txt" file

# make sure the file is made new with our loop
if (file.exists(textfile_co)) {file.remove(textfile_co)}

# make sure the file is made new with our loop
if (file.exists(textfile_mp)) {file.remove(textfile_mp)}

for(line in 1:length(db_ET_MP$n_1)){
  if(!is.na(db_ET_MP[line,]$t)){
    newline = paste("t(", db_ET_MP[line,]$n_1-1, ")=",db_ET_MP[line,]$t, sep = "")
    write(newline, file = textfile_mp, append = TRUE)
    #cat("\n")
    #write(newline, file = textfile, append = TRUE)    
  }
}

```{r Power_exist_descript, echo = FALSE}
d = rma.mv(g_calc, g_var_calc, data = db_mpe, random = ~ 1 | short_cite)$b[,1]

# estimate from mispronunciation sensitivity
mp_est <- round(coef(summary(rma_MPeffect))[2,]$estimate, 2)

# one-sided t-test
ptt <- pwr.t.test(d = mp_est, sig.level = .05, type = "paired", power = .80, alternative = "greater")

The median sample size across studies in our dataset was `r median(db_mpe$n_1, na.rm=TRUE)`. To study infants' mispronunciation senstivity, which we estimate to have an effect size of `r mp_est`, this test gives the number of participants (n = `r round(ptt$n, 2)`) required in a within-participant design using a one-sided t-test to conduct a study which has 80% power.

```{r Power_plan, echo = FALSE}
